---
title: "November curse"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
date: "April 17, 2018"
---

NULL HYPOTHESIS -  Mean losses for London teams in NOVEMBER is not more than mean losses in NOVEMBER for other teams.
ALTERNATIVE HYPOTHESIS - Mean losses for London teams in NOVEMBER is more than mean losses in NOVEMBER for other teams.

Read the loss and master dataset
```{r}
library(readr)
library(dplyr)
Team_loss <- read_csv("C:/RPROJECT/Team_loss.csv")
Team_master <- read_csv("C:/RPROJECT/Team_match_master.csv")
```

Aggregate losses in November by LONDON teams and OTHER teams
```{r}
Team_loss_n = Team_master %>%
  select(Team_Name,Month_Name,Month,Result) %>%
  group_by(Team_Name,Month_Name,Month) %>%
  summarise(Loss=sum(Result=="Lose")) %>%
  arrange(Month)

Team_loss_nov_lo = subset(Team_loss_n,Month_Name =='NOV' & (Team_Name == "Chelsea" | Team_Name == "Arsenal" | Team_Name == "Fulham" | Team_Name == "Tottenham Hotspur" | Team_Name == "Queens Park Rangers"))

Team_loss_nov_oth = subset(Team_loss_n,Month_Name =='NOV' & (Team_Name != "Chelsea" & Team_Name != "Arsenal" & Team_Name != "Fulham" & Team_Name != "Tottenham Hotspur" & Team_Name != "Queens Park Rangers"))
```

Calculate sample mean and standard deviation and N
```{r}
lo_mean = mean(Team_loss_nov_lo$Loss)
lo_sd = sd(Team_loss_nov_lo$Loss)

oth_mean = mean(Team_loss_nov_oth$Loss)
oth_sd = sd(Team_loss_nov_oth$Loss)

lo_n = length(Team_loss_nov_lo$Loss)
oth_n = length(Team_loss_nov_oth$Loss)
```

T statistic calculation
```{r}
a = lo_mean - oth_mean
b = (lo_n - 1) * (lo_sd^2)
c = (oth_n - 1) * (oth_sd^2)
d = (lo_n + oth_n) -2
sp = (b + c) /d
e = sqrt((sp/lo_n) + (sp/oth_n))

tstat = (a-0)/e
tstat
```

Critical T value
```{r}
tcrit = qt(p = 0.1,df = (lo_n+oth_n-2),lower.tail = F)
tcrit
```

Since this is an upper tail test, we reject the NULL HYPOTHESIS with a 90% CONFIDENCE and conclude that there is enough evidence to say that LONDON TEAMS tend to lose more in NOVEMBER than other teams.
